Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-12 manuscript/draft.Rmd
re-arrange Data section

Bird species richness was obtained from the Breeding Bird Survey (BBS)
[@pardieck2017] using the Data Retriever software [@morris2013] and
rdataretriever R package [@mcglinn2017]. The BBS data was filtered to exclude
all nocturnal, cepuscular, and aquatic species [since these species are not well
sampled by BBS methods; @hurlbert2005], as well as unidentified species, and
hybrids. Due to limitations of the environmental data (below), we did not
include any data from outside the continental United States. Observed richness
from 1982 (the first complete year of NDVI data) to 2003 were used for training
the models, and data from 2004 to 2013 was used for testing their performance.
Only BBS routes that were sampled during 70% of the years in the training period
were used (i.e., routes with at least 16 annual observations). All data from
routes that did not meet BBS acceptable criteria were excluded, as were routes
that had not been visited during at least 70% of the years in our model-training
window. The resulting dataset included [[N]] species and [[N]] sites. Among
sites,  richness varied from [[N]] to [[N]] with an average richness of [[N]]
species.

@@

>>>>

Bird species richness was obtained from the North American Breeding Bird Survey
(BBS) [@pardieck2017] using the Data Retriever software [@morris2013] and
rdataretriever R package [@mcglinn2017]. The BBS data was filtered to exclude
all nocturnal, cepuscular, and aquatic species [since these species are not well
sampled by BBS methods; @hurlbert2005], as well as unidentified species, and
hybrids. All data from routes that did not meet BBS acceptable criteria were
also excluded.

@@

We used observed richness values from 1982 (the first complete year of NDVI
data) to 2003 for training the models, and data from 2004 to 2013 was used for
testing their performance. We only used BBS routes from the continental United
States (i.e. routes where PRISM data was available), and restricted the analysis
to routes that were sampled during 70% of the years in the training period were
used (i.e., routes with at least 16 annual observations). The resulting dataset
included [[N]] transect runs of [[N]] unique sites, and included [[N]] species.
Site-level richness varied from [[N]] to [[N]] with an average richness of [[N]]
species.
